\documentclass[11pt, letterpaper]{article}

% Packages
\usepackage[margin=1in, top=0.8in, bottom=0.8in]{geometry}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{microtype}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

% Hyperlink colors
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black
}

% Section formatting (bold, with horizontal rule, like Chaerim Moon's CV)
\titleformat{\section}
  {\large\bfseries}
  {}
  {0em}
  {}
  [\titlerule]
\titlespacing{\section}{0pt}{10pt}{4pt}

% No paragraph indent
\setlength{\parindent}{0pt}

% Custom commands
\newcommand{\cventry}[3]{%
  \noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
    \textbf{#1} & #2
  \end{tabular*}\\
  #3\par\vspace{4pt}
}

\begin{document}

% ─── Header ───────────────────────────────────────────────────────────────────
\begin{center}
  {\LARGE\bfseries Paul Son}\\[4pt]
  50 Field House Dr \#B206, Baton Rouge, LA 70802\\[2pt]
  \faHome\ \href{https://pauldongin.github.io}{pauldongin.github.io}\quad
  \faGraduationCap\ \href{https://scholar.google.com/citations?hl=en&user=YOURID}{Google Scholar}\quad
  \faEnvelope\ \href{mailto:dson2@lsu.edu}{dson2@lsu.edu}
\end{center}

\vspace{6pt}

% ─── Research Interest ────────────────────────────────────────────────────────
\section{Research Interest}

Physical activity, sedentary behavior, screen time

% ─── Education ────────────────────────────────────────────────────────────────
\section{Education}

\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Louisiana State University}, \textit{Baton Rouge, LA} & 2024 -- Present
\end{tabular*}\\
Ph.D.\ in Kinesiology, School of Kinesiology
(Minor: Applied Statistics)\\
Advisor: Dr.\ Chen, S.

\vspace{6pt}

\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Korea University}, \textit{Seoul, South Korea} (GPA: 4.5/4.5) & 2018 -- 2021
\end{tabular*}\\
M.S.\ in Physical Education\\
Supervisor: Dr.\ Yu, T.\ H.\\
Thesis: \textit{Qualitative research on physical education major students' experience of double major}

\vspace{6pt}

\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Korea University}, \textit{Seoul, South Korea} (GPA: 3.99/4.5) & 2012 -- 2018
\end{tabular*}\\
B.S.\ in Physical Education

% ─── Publications ─────────────────────────────────────────────────────────────
\section{Publications}

\textbf{Peer-Reviewed Journal Articles}

\begin{enumerate}[leftmargin=*, label=\arabic*., itemsep=4pt]

  \item \textbf{Son P}, Nie Y, Tan Q, Yang P, Murray P, et al.\ (2026). Variations in children's screen time behaviors by weight status among a mostly disadvantaged population. \textit{PLOS ONE}, 21(4): e0346235. \href{https://doi.org/10.1371/journal.pone.0346235}{https://doi.org/10.1371/journal.pone.0346235}

  \item Tan Q, Nie Y, \textbf{Son P}, Qian Y, Staiano AE, Wang F, \ldots{} \& Chen S. (2026). Using AI chatbot to assist students' behavior management for obesity prevention in middle schools: Feasibility study. \textit{JMIR Formative Research}, 10(1), e83630.

  \item \textbf{Son P}, Nie Y, Tan Q, Staiano AE, Wang F, Hu G, Gordon S, Murray P, Luo C, Zeng Y, Underwood RA \& Chen S. (2026). Health behaviors and social determinants of health in children from under-resourced communities: does weight status play a role? \textit{Frontiers in Sports and Active Living}, 7:1695539. \href{https://doi.org/10.3389/fspor.2025.1695539}{doi: 10.3389/fspor.2025.1695539}

  \item Nie Y, Tan Q, \textbf{Son P}, Staiano AE, Rosenkranz RR, Spring KE, \ldots{} \& Chen S. (2025). Testing an adapted obesity prevention intervention in under-resourced schools: a pilot clustered randomized controlled trial. \textit{Scientific Reports}, 15(1), 31678.

  \item Tan Q, Nie Y, \textbf{Son P}, Underwood RA, Murray P, Hebert C, McKey KL, Hendrick C, Staiano AE \& Chen S. (2024). Preliminary effectiveness of a one-week summer day camp for improving children's health behaviors and psychosocial well-being outcomes. \textit{Children}, 11(9), 1097. \href{https://doi.org/10.3390/children11091097}{https://doi.org/10.3390/children11091097}

  \item \textbf{Son DI} \& Park JH. (2021). Qualitative research on physical education major students' experience of double major. \textit{The Korean Journal of Physical Education}, 60(6), 55--69.

  \item \textbf{Son DI}, Hwang YH \& Yu TH. (2016). A study on the freshmen welcome party of physical education major students. \textit{Korean Society for the Sociology of Sport}, 29(1), 19--44.

\end{enumerate}

% ─── Academic Presentations ───────────────────────────────────────────────────
\section{Academic Presentations}

\textbf{Oral Presentations}

\begin{itemize}[leftmargin=*, itemsep=3pt]
  \item Chen S \& \textbf{Son P}. (March 13, 2024). \textit{Feasibility of the ProudME Intervention: A case of the Whole-of-School Initiative.} 2024 SHAPE America National Convention \& Expo, Cleveland, Ohio.

  \item \textbf{Son DI} \& Yu TH. (October 5, 2019). \textit{A qualitative research on physical education major students' experience of double major.} 57th KAPHERD Conference for the 100th National Sports Festival Commemoration, Yonsei University, Seoul, South Korea.
\end{itemize}

\vspace{4pt}
\textbf{Poster Presentations}

\begin{itemize}[leftmargin=*, itemsep=3pt]
  \item \textbf{Son P}. (June 12, 2025). \textit{Children's Health Behavior Vary by Social Determinants of Health.} 2025 International Society of Behavioral Nutrition and Physical Activity, Oakland, New Zealand.
\end{itemize}

% ─── Teaching Experience ──────────────────────────────────────────────────────
\section{Teaching Experience}

\textbf{Graduate Teaching Assistant}, \textit{Louisiana State University}

\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  KIN 3502 Test and Measurement in Kinesiology (Lab) & Spring 2026 \\
  KIN 3502 Test and Measurement in Kinesiology (Lab) & Fall 2025 \\
  KIN 1999 Pickleball & Spring 2025 \\
  KIN 3502 Test and Measurement in Kinesiology (Lab) & \\
  KIN 1999 Pickleball & Fall 2024 \\
  KIN 3502 Test and Measurement in Kinesiology (Lab) & \\
  KIN 1999 Pickleball & Spring 2024 \\
\end{tabular*}

\vspace{6pt}
\textbf{Volunteer Tutor}, \textit{Seoul National University High School}, Seoul, South Korea \hfill Spring 2016\\
Taught mathematics to underserved high school students.

% ─── Research Experience ──────────────────────────────────────────────────────
\section{Research Experience}

\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Research Assistant} & 2019
\end{tabular*}\\
Title: \textit{Physical education textbook translation project} (PI: Dr.\ Yu, T.\ H.)\\
Textbook: Rink, J.\ (2014). \textit{Teaching Physical Education for Learning} (7th ed.). McGraw-Hill.
\begin{itemize}[leftmargin=2em, itemsep=1pt, topsep=2pt]
  \item Wrote manuscript chapters on motivation, student growth, planning, and evaluation in physical education
\end{itemize}

\vspace{4pt}
\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Research Assistant} & 2015
\end{tabular*}\\
Title: \textit{Sport hero interview project}\\
Funding: Korean Sport \& Olympic Committee
\begin{itemize}[leftmargin=2em, itemsep=1pt, topsep=2pt]
  \item Participated in meetings and research presentations and transcribed interview recordings of sport heroes selected by the Korea Sport \& Olympic Committee

\end{itemize}

% ─── Award / Scholarship ──────────────────────────────────────────────────────
\section{Award / Scholarship}

\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Travel Award} (approx.\ 2,300 USD), \textit{College of Education, Korea University} & Winter 2015
\end{tabular*}\\
Title: \textit{A study on collegiate recreational sports}
\begin{itemize}[leftmargin=2em, itemsep=1pt, topsep=2pt]
  \item Conducted comparative analysis of intramural sport in South Korea and the United States
  \item Interviewed representatives of Recreational Sport at the Ohio State University, Columbus, OH
\end{itemize}

\vspace{4pt}
\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Travel Award} (Full travel expense), \textit{AEON Group Foundation, Japan} & Summer 2014
\end{tabular*}\\
Asian Students Environment Platform (ASEP) 2014, Tsinghua University, China
\begin{itemize}[leftmargin=2em, itemsep=1pt, topsep=2pt]
  \item Wrote pre-assignment on water sources in Korea
  \item Visited cities related to water sources in China affecting the ecosystem
  \item Participated in tree plantation activity in the desert
  \item Prepared and delivered an oral presentation jointly with students from China, Japan, Malaysia, and Vietnam
\end{itemize}

% ─── Working Experience ───────────────────────────────────────────────────────
\section{Working Experience}

\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Physical Activity Instructor}, \textit{Seoil Elementary School}, Seoul, South Korea & Fall 2018
\end{tabular*}\\
Taught recreational physical activities to children aged 6 to 7.

\vspace{4pt}
\noindent\begin{tabular*}{\textwidth}{@{}l@{\extracolsep{\fill}}r@{}}
  \textbf{Physical Activity Instructor}, \textit{Viva Sports Academy}, Seoul, South Korea & 2012 -- 2013
\end{tabular*}\\
Trained high school students preparing for the Kinesiology major entrance exam.

% ─── Skills ───────────────────────────────────────────────────────────────────
\section{Skills}

\textbf{Statistical Analysis:} IBM SPSS, RStudio\\
\textbf{Geographic Information Systems (GIS):} ArcGIS

  % ─── Languages ────────────────────────────────────────────────────────────────
  \section{Languages}

  \begin{itemize}[leftmargin=*, itemsep=2pt]
    \item Korean -- Native Speaker
    \item English -- Full Professional Proficiency
    \item Japanese -- Professional Working Proficiency (JLPT N1)
  \end{itemize}

\end{document}
